A systematic comparison of interaction models for systems of cities

### 2018-09-20 Docs/CCS18/Communication/ccs2018.tex
runmarius

@@

@@

@@

Raimbault, J. (2018). Caractérisation et modélisation de la co-évolution des réseaux de transport et des territoires (Doctoral dissertation, Université Paris 7 Denis Diderot). \url{https://halshs.archives-ouvertes.fr/tel-01857741}

>>>>

\sframe{Network interaction model}{

% increasing complexity for the presentation of models

\sframe{The Favaro-Pumain model}{

@@

Harmonized dataset, explored in particular by \cite{pumain2015multilevel} (built by

@@

% number of runs (equivalent / year) ; caracs of NSGA2 ; convergence for each model/system

\sframe{Results: comparison of models on the different systems}{

% global overview : Pareto plots / tabular of % effective pareto front for each system
% (requires the extraction of effective fronts)

\sframe{Results: particular cases}{

% systems on which the behavior is particularly interesting ?

%\sframe{Results: influence of parameters}{
% add if cool results
%}

\sframe{Results: empirical AIC}{
% TODO : select optimal points / run empirical AIC
% OR : run on all points of the Pareto front ? -> local OK

@@

Raimbault, J. (2018). Caract{\'e}risation et mod{\'e}lisation de la co-{\'e}volution des r{\'e}seaux de transport et des territoires (Doctoral dissertation, Université Paris 7 Denis Diderot). \url{https://halshs.archives-ouvertes.fr/tel-01857741}
